beautier: BEAUti for R

### 2017-12-23 article.tex
Use beauter v1.12.1 interface

Novel about \verb;beautier; is that it allows for specifying a fixed crown age. 
By default, a phylogeny's crown age is jointly estimated with the other parameters.
Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age is \verb;beautier;:

\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
create_beast2_input_file(
  "alignment.fas",
  "beast2.xml"
  fixed_crown_ages = TRUE,
  initial_phylogenies = fasta_to_phylo(
    fasta_filename = "alignment.fas", 
    crown_age = 15
  )
)
\end{lstlisting}

This code shows that setting \verb;fixed_crown_age; to true is insufficient. An
initial phylogeny of the desired (fixed) crown age needs to be supplied. In this
example, a random phylogeny is constructed from the FASTA filename. Supplying an 
informed phylogeny will make the MCMC algorithm start at a likelier initial state.

>>>>

Novel about \verb;beautier; is that it allows for specifying a fixed crown age. 
By default, a phylogeny's crown age is jointly estimated with the other parameters.
Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age with \verb;beautier;:

\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
create_beast2_input_file(
  "alignment.fas",
  "beast2.xml"
  crown_age = 15
)
\end{lstlisting}
